``FISTA'' in Banach spaces with adaptive discretisations

### 2021-09-24 response.tex

	\item \review{page 12 and elsewhere: $\partial E$ is usually referred to as the subdifferential. I suppose this depends on the literature source you use.}

	As suggested, we have switched to using the term `subdifferential' throughout the document.

	\item \review{My only ``disappointment'' with the paper is that the theory is illustrated with LASSO. As a result, $E$ has a rather favorable structure. There are many examples, e.g., in robust statistics, where it would be more appropriate to use the $\ell^1$ norm instead of the $\ell^2$ norm for misfit. Since the favorable properties of the squared $\ell^2$-norm are often used in the derivations (bounds, constants, etc. in Section 6), I wonder how hard it would be to do the same for other relevant examples.}

	You are right, we can also consider alternative misfits. We have replaced the wavelet example with a (Huber-smoothed) robust $\ell^1$ penalty as we only explicitly required the gradient and Lipschitz constant for computations.

@@

	Thank you for noticing this typo.

	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity. The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions. While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
\end{enumerate}

\section{Detailed response to second reviewer}
We are very sorry that you found our manuscript so difficult to read. You were right, the former foundations were not rigorous enough. We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space. The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space. Consequently, we also realised that the orthogonal projection was not needed at all, and we now allow $U^n$ to be subsets of $\F H$ rather than subspaces. The Banach space setting is reserved for examples discussed in Sections 5 to 7.

### 2021-09-24 paper.tex
First edits for Antonin, removed ortho projection

\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\newcommand{\1}{\F{1}}
\DeclareMathOperator{\st}{\;s.t.\;}
\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

% Macro for tracking changes
\usepackage[normalem]{ulem}\renewcommand{\ULthickness}{1.0pt}
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
%\renewcommand{\edit}[2]{#2}

@@

	\begin{abstract}
		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever the \edit{optimisation domain}{optimiser} is contained in a suitable Hilbert space. We propose a modified algorithm where each iteration is performed in a subspace, and that subspace is allowed to change at every iteration. Analytically, this allows us to guarantee convergence in a Banach space setting, although at a reduced rate depending on the conditioning of the specific problem. Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.
	\end{abstract}
	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}

@@

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining }{closed }subspaces $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the subspace $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.

	Without loss of generality we will assume $L=1$, i.e. $\nabla\op{f}$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
	\begin{equation}
		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
	\end{equation}
	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
	\begin{equation}
		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
	\end{equation}
	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$. \edit{}{We denote the orthogonal projection operators $\tens{\Pi}_n\colon\F H\to\spcf0^n$ such that $\tens{\Pi}_n\varf0-\varf0 \perp \varf1$ for all $\varf0\in\F H$, $\varf1\in\spcf0^n$. \todo{Finite dimensional?}}

@@

	\begin{algorithm}\caption{Refining subspace FISTA}\label{alg: refining FISTA}
		\centering
		\begin{algorithmic}[1]
			\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
			\State $\varf1_0\gets \varf0_0, n\gets0$
			\Repeat
			\State $\bar{\varf0}_n \gets (1-\tfrac{1}{t_n})\varf0_n + \tfrac{1}{t_n}\varf1_n$
			\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \op{f}(\bar{\varf0}_n)}^2+\op{g}(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
			\State $\varf1_{n+1} \gets (1-t_n)\varf0_n + t_n\varf0_{n+1}$
			\State $n\gets n+1$
			\Until{converged}
		\end{algorithmic}
	\end{algorithm}

@@

	\paragraph{Step 1: Quantifying the stability}
	\begin{adaptiveStep}\label{step: step 1 stability}
		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting subspaces $\spcf0^n$. In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that 
		\begin{equation}\label{eq: mini FISTA convergence}
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
		\end{equation}
		for any $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$. The similarities to \eqref{eq: classical FISTA} are clear. If $\spcf0^n=\edit{\spcf0}{\F H}$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the two estimates agree. These extra terms quantify the robustness to changing of discretisation.
	\end{adaptiveStep}

	\paragraph{Step 2: Quantifying the scaling properties}
	\begin{adaptiveStep}\label{step: step 2 smoothness}
		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$. To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
		\begin{equation}
			n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \op{E}_0(\varf2_n) \lesssim \vars3_{\op{E}}^{-k}.
		\end{equation}
		The choice of exponential scaling is very natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh. If that mesh sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$. The integer $n_k$ should then be the time when the mesh has refined $k$ times.

@@

	\paragraph{Step 3: Generalising the convergence bound}
	\begin{adaptiveStep}\label{step: step 3 convergence bound}
		In this step we combine the FISTA stability estimate with the subspace approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$. For example, if $\spcf0^n$ is of the form 
		$$ \spcf0^{n_k} = \spcf0^{n_k+1} = \ldots = \spcf0^{n_{k+1}-1},$$
		then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0. The result of this is presented in Lemma~\ref{thm: mini exponential FISTA convergence} but the moral is that the stability error in \eqref{eq: mini FISTA convergence} should scale in proportion to the $k$ (related to the resolution) rather than the total number of iterations $N$.
	\end{adaptiveStep}

	\paragraph{Step 4: Sufficiently fast refinement}
	\begin{adaptiveStep}\label{step: step 4 sufficiently fast}
		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor. In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed subspace $\spcf0^N$. The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$. Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\spcf0^n$ refine sufficiently quickly, i.e. $n_k$ are sufficiently small.
	\end{adaptiveStep}

	\paragraph{Step 5: Sufficiently slow refinement}
	\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate. If the subspaces refine too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence. If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow. Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of 
		$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\op{E}}$. In particular, if \edit{$\varf0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
	\end{adaptiveStep}

@@

	\subsection{Computing the convergence bound}
	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}. The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely.

	\edit{}{Throughout this section we consider a sequence of subspaces $\spcf0^n$ which generate the iterates $\varf0_n$ in Algorithm~\ref{alg: refining FISTA} satisfying
		\begin{equation}\label{eq: refining subspace definition}
			\spcf0^n\subset\F H \text{ for } n\in\F N \qquad\text{such that}\qquad \spcf0^n \text{ is closed and }\varf0_n\in\spcf0^{n+1}\text{ for all }n\in\F N
		\end{equation}
		with orthogonal projections $\tens{\Pi}_n\colon\F H\to\spcf0^n$.
	}

	\subsubsection{Single iterations}
	We first wish to understand a single iteration of Algorithm~\ref{alg: refining FISTA}. This is done through the following two lemmas.
	\begin{lemma}[equivalent to {\cite[Lemma \edit{1}{3.1}]{Chambolle2015}}]\label{thm: descent lemma}
		\Copy{thm: descent lemma}{
			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\varf0}\in \edit{\spcf0^{n}}{\F H}$ define
			$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \op{f}(\bar{\varf0})}^2+\op{g}(\varf0).$$
			Then, for all $\varf2\in\edit{\bar{(\spcf0^n)^*}\supset\F H}{\spcf0^n}$, we have
			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\tens{\Pi}_n\bar{\varf0}-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
		}
	\end{lemma}
\todo{check this}
	\noindent This is exactly the result of \cite{Chambolle2015} applied to the function $\varf0\mapsto\op{E}(\tens{\Pi}_n\varf0)$. Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.

@@

	\begin{theorem}[\edit{}{analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}}]\label{thm: mini FISTA convergence}
		\Copy{thm: mini FISTA convergence}{
			Fix a sequence of subspaces $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$. Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
		}
		\begin{equation}\label{eq: FISTA inequality}\Copy{thm:eq: mini FISTA convergence}{
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
		}\end{equation}
	\end{theorem}
	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}. This result is the key approximation for showing convergence of FISTA with refining subspaces. In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.

>>>>

\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\newcommand{\1}{\F{1}}
\DeclareMathOperator{\st}{\;s.t.\;}
\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}

@@

% Macro for tracking changes
\usepackage[normalem]{ulem}\renewcommand{\ULthickness}{1.0pt}
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
%\renewcommand{\edit}[2]{#2}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

	\begin{abstract}
		FISTA is a popular convex optimisation algorithm which is known to converge at an optimal rate whenever \edit{the optimisation domain}{a minimiser} is contained in a suitable Hilbert space. We propose a modified algorithm where each iteration is performed in a \edit{subspace, and that subspace is allowed to change at every iteration}{subset which is allowed to change at every iteration}. \edit{Analytically, this allows us to guarantee convergence in a Banach space setting}{Sufficient conditions are provided for guaranteed convergence}, although at a reduced rate depending on the conditioning of the specific problem. \edit{Numerically we show that a greedy adaptive choice of discretisation can greatly increase the time and memory efficiency in infinite dimensional Lasso optimisation problems.}{These conditions have a natural interpretation when a minimiser exists in an underlying Banach space. A typical example is the Lasso problem where we provide detailed theoretical and numerical analysis.}
	\end{abstract}
	\keywords{Convex optimization \and Multiscale \and Multigrid \and Sparsity \and Lasso}

@@

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n=0,1,\ldots$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$ then we recover the \edit{standard FISTA}{original} algorithm.

	Without loss of generality we will assume $L=1$, i.e. $\nabla\op{f}$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
	\begin{equation}
		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
	\end{equation}
	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
	\begin{equation}
		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
	\end{equation}
	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$. \edit{}{Note in particular we need the argmin to be non-empty. For this we will assume $\spcf0^n$ are locally compact, for example finite dimensional.}

@@

	\begin{algorithm}\caption{Refining \edit{subspace}{subset} FISTA}\label{alg: refining FISTA}
		\centering
		\begin{algorithmic}[1]
			\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
			\State $\varf1_0\gets \varf0_0, n\gets0$
			\Repeat
			\State $\bar{\varf0}_n \gets (1-\tfrac{1}{t_n})\varf0_n + \tfrac{1}{t_n}\varf1_n$
			\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \op{f}(\bar{\varf0}_n)}^2+\op{g}(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
			\State $\varf1_{n+1} \gets (1-t_n)\varf0_n + t_n\varf0_{n+1}$
			\State $n\gets n+1$
			\Until{converged}
		\end{algorithmic}
	\end{algorithm}

@@

	\paragraph{Step 1: Quantifying the stability}
	\begin{adaptiveStep}\label{step: step 1 stability}
		The first step is to generalise \eqref{eq: classical FISTA} to account for the adapting \edit{subspaces}{subsets} $\spcf0^n$. In the notation of Algorithm~\ref{alg: refining FISTA}, Theorem~\ref{thm: mini FISTA convergence} shows that 
		\begin{equation}\label{eq: mini FISTA convergence}
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf2_N}^2 \leq \tfrac12\norm{\varf0_0-\varf2_0}^2 +\tfrac{\norm{\varf2_N}^2-\norm{\varf2_0}^2}2 
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}
		\end{equation}
		for any $\varf2_n \in \argmin_{\varf0\in\spcf0^n}\op{E}(\varf0)$. The similarities to \eqref{eq: classical FISTA} are clear. If $\spcf0^n=\edit{\spcf0}{\F H}$, then we have $\varf2_n=\edit{\varf0^*}{\varf2_0\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the two estimates agree. These extra terms quantify the robustness to changing of discretisation.
	\end{adaptiveStep}

	\paragraph{Step 2: Quantifying the scaling properties}
	\begin{adaptiveStep}\label{step: step 2 smoothness}
		To show that the extra terms in \eqref{eq: mini FISTA convergence} are small, we need to quantify the approximation properties of $\spcf0^n$. To do so, we construct a secondary sequence $n_0 < n_1 < \ldots$ and constants $\vars3_{\Varf0},\vars3_{\op{E}}\geq1$ such that for each $k\in\F N$
		\begin{equation}
			n\leq n_k \implies \norm{\varf2_n} \lesssim \vars3_{\Varf0}^k, \qquad n\geq n_k \implies \op{E}_0(\varf2_n) \lesssim \vars3_{\op{E}}^{-k}.
		\end{equation}
		The choice of exponential scaling is very natural if we consider the $\spcf0^n$ to be the subspace of functions discretised on a uniform mesh. If that mesh sequentially refined, then the resolution of the mesh will be of order $h^k$ after $k$ refinements and for some $h<1$. The integer $n_k$ should then be the time when the mesh has refined $k$ times.\edit{}{ Another canonical choice would be $\spcf0^n=\{\varf0\in\F H\st \norm{\varf0}\leq \vars3_{\Varf0}^k\}$. The exponential scaling is less natural, but leads to better convergence guarantees.}

@@

	\paragraph{Step 3: Generalising the convergence bound}
	\begin{adaptiveStep}\label{step: step 3 convergence bound}
		In this step we combine the FISTA stability estimate with the \edit{subspace}{subset} approximation guarantees to provide a sharper estimate of stability with respect to the parameters $\vars3_{\op{E}}$ and $\vars3_{\Varf0}$. For example, if $\spcf0^n$ is of the form 
		$$ \spcf0^{n_k} = \spcf0^{n_k+1} = \ldots = \spcf0^{n_{k+1}-1},$$
		then many terms on the right-hand side of \eqref{eq: mini FISTA convergence} telescope to 0. The result of this is presented in Lemma~\ref{thm: mini exponential FISTA convergence} but the moral is that the stability error in \eqref{eq: mini FISTA convergence} should scale in proportion to the $k$ (related to the resolution) rather than the total number of iterations $N$.
	\end{adaptiveStep}

	\paragraph{Step 4: Sufficiently fast refinement}
	\begin{adaptiveStep}\label{step: step 4 sufficiently fast}
		In Step~\ref{step: step 3 convergence bound} we developed a convergence bound, now we wish to show that it is only worse than the classical \eqref{eq: classical FISTA} by a constant factor. In particular, it is equivalent to run Algorithm~\ref{alg: refining FISTA} for $N$ iterations or the classical FISTA algorithm for $N$ iterations on the fixed \edit{subspace}{subset} $\spcf0^N$. The estimate from \eqref{eq: classical FISTA} provides the estimate $N^2\op{E}_0(\varf0_N)\lesssim \norm{\varf0_0-\varf2_N}^2 = O(\vars3_{\Varf0}^{2K})$ for $N\leq n_K$. Lemma~\ref{thm: sufficiently fast} shows that Algorithm~\ref{alg: refining FISTA} can achieve the same order of approximation, so long as $\spcf0^n$ refine sufficiently quickly, i.e. $n_k$ are sufficiently small.
	\end{adaptiveStep}

	\paragraph{Step 5: Sufficiently slow refinement}
	\begin{adaptiveStep}\label{step: step 5 sufficiently slow}
		The result of Step~\ref{step: step 4 sufficiently fast} is sufficient to prove convergence, but not yet a rate. If the \edit{subspaces refine}{subsets grow} too quickly, then the influence of \edit{$\norm{\varf0^*}=\infty$}{$\norm{\varf0_n}\to\infty$} will slow the rate of convergence. If the resolution is too coarse then we are overfitting to the discretised problem, but if the resolution is too fine then convergence of the energy is slow. Lemma~\ref{thm: sufficiently slow} balances these two factors in an optimal way for Algorithm~\ref{alg: refining FISTA} resulting in a convergence rate of 
		$$ \op{E}_0(\varf0_N) \lesssim \frac{\vars3_{\Varf0}^{2K}}{N^2} \lesssim \frac{N^{2\kappa}}{N^2}$$
		for all $N\in\F N$, some $\kappa\in[0,1)$ depending on $\vars3_{\Varf0},\vars3_{\op{E}}$. In particular, if \edit{$\varf0^*\in\F H$}{the minimum is attained in $\F H$,} then we recover the classical rate with $\kappa=0$.
	\end{adaptiveStep}

@@

	\subsection{Computing the convergence bound}
	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}. The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely. 
	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} satisfying
	\begin{equation}\label{eq: refining subspace definition}
		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{are closed, convex, locally compact subsets for all }\quad n\in\F N.
	\end{equation}}

	\subsubsection{Single iterations}
	We first wish to understand a single iteration of Algorithm~\ref{alg: refining FISTA}. This is done through the following two lemmas.
	\begin{lemma}[equivalent to {\cite[Lemma \edit{1}{3.1}]{Chambolle2015}}]\label{thm: descent lemma}
		\Copy{thm: descent lemma}{
			Suppose $\nabla \op{f}$ is 1-Lipschitz, for any $\bar{\varf0}\in \edit{\spcf0^{n}}{\F H}$ define
			$$ \varf0 \coloneqq \argmin_{\varf0\in \spcf0^{n}} \tfrac12\norm{\varf0-\bar{\varf0}+\nabla \op{f}(\bar{\varf0})}^2+\op{g}(\varf0).$$
			Then, for all $\varf2\in\edit{\bar{(\spcf0^n)^*}\supset\F H}{\spcf0^n}$, we have
			\edit{\\\centerline{$\displaystyle \op{E}(\varf0) + \tfrac12\norm{\varf0-\tens{\Pi}_n\varf2}^2 \leq \op{E}(\tens{\Pi}_n\varf2) + \tfrac12\norm{\bar{\varf0}-\tens{\Pi}_n\varf2}^2.$}}{
			$$\op{E}(\varf0) + \tfrac12\norm{\varf0-\varf2}^2 \leq \op{E}(\varf2) + \tfrac12\norm{\bar{\varf0}-\varf2}^2.$$}
			\edit{where $\tens{\Pi}_n\colon\bar{(\spcf0^n)^*}\to\spcf0^n$ is the orthogonal projection.}{}
		}
	\end{lemma}
	\noindent This is exactly the result of \cite{Chambolle2015} on the \edit{subspace}{subset} $\spcf0^n$. Applying Lemma~\ref{thm: descent lemma} to the iterates from Algorithm~\ref{alg: refining FISTA} gives a more explicit inequality.

@@

	\begin{theorem}[\edit{}{analogous to {\cite[Thm 3.2]{Chambolle2015}, \cite[Thm 4.1]{Beck2009}}}]\label{thm: mini FISTA convergence}
		\Copy{thm: mini FISTA convergence}{
			Fix a sequence of \edit{subspaces}{subsets} $(\spcf0^n\edit{\subset\spcf0\cap\F H}{})_{n\in\F N}$ \edit{}{satisfying \eqref{eq: refining subspace definition}}, arbitrary $\varf0_0\in \spcf0^0$, and FISTA stepsize choice $(t_n)_{n\in\F N}$. Let $\varf0_n$ and $\varf1_n$ be generated by Algorithm~\ref{alg: refining FISTA}, then, for any choice of $\varf2_n\in\spcf0^n$ and $N\in\F N$ we have
		}
		\begin{equation}\label{eq: FISTA inequality}\Copy{thm:eq: mini FISTA convergence}{
			t_N^2\op{E}_0(\varf0_N) + \sum_{n=1}^{N-1}\rho_n \op{E}_0(\varf0_n) + \frac{\norm{\varf1_N-\varf2_N}^2}{2} \leq \frac{\norm{\varf0_0-\varf2_0}^2-\norm{\varf2_0}^2+\norm{\varf2_N}^2}{2}
			+ \sum^N_{n=1} t_n\op{E}_0(\varf2_n) + \IP{\varf1_{n-1}}{\varf2_{n-1}-\varf2_n}.
		}\end{equation}
	\end{theorem}
	\noindent The proof is given in Theorem~\ref{app:thm: mini FISTA convergence}. This result is the key approximation for showing convergence of FISTA with \edit{refining subspaces}{growing subsets}. In the classical setting, we have $\spcf0^n\edit{=\spcf0}{}=\F H$, $\varf2_n\edit{=\varf0^*}{\in\argmin_{\varf0\in\F H}\op{E}(\varf0)}$ and the extra terms on the right-hand side collapse to 0.
